A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
remove todo
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1018 43ef1190-90fd-4dd7-a769-d0121f02b80e
15 pages now
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1019 43ef1190-90fd-4dd7-a769-d0121f02b80e

We used SPARQLES survey list of SPARQL endpoints as of 2014-11-17, and
filtered out those deemed unresponsive by them. This resulted in a
list of 312 endpoints.

@@

We obtained a successful response from a total 2965 information
resources, either with SPARQL results or RDF data. A successful
response is rather strictly defined, not only must there be a
successful HTTP response after redirects are resolved, the response
must also return a valid RDF media type (unless it is a SPARQL result)
and the response must parse into an RDF model. We have given priority
to survey many hosts since configuration usually doesn't differ much
across a host, especially since it also captures different types of
resources. It is therefore acceptable that the number of resources is
relatively small.

@@

In Figure~\ref{fig:hardtable}\todo{look for others or explain, colors}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification \cite{voidnote} also notes that the
statistics are considered estimates.

@@

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\footnote{https://metacpan.org/release/KJETILK/RDF-Generator-HTTP-0.003}
to the Comprehensive Perl Archive Network. We recorded whether the
conditional request showed that the BTC data were still fresh, and if
it was, we retrieved the current data, as we had not coupled the
headers to the body in our original retrieval.

Based on the resulting headers, we let
libwww\footnote{https://metacpan.org/release/GAAS/libwww-perl-6.04}
calculate both standards-compliant and simple heuristic freshness
lifetime.

If the initial response had RFC7232 headers, we make another
request to see if the server just included the headers but does not
actually support conditional requests. The heuristic we employed is
that if the headers remain the same, but the result was returned,
rather than just a response code \httph{304} (which indicates that the
previous result can be reused), then the server does most probably not
support it.

For endpoints, we examined the response message, to see if there are
any results to our query, and recorded that if there are. In addition
to the endpoints registered in the SPARQLES survey, our process found
18~endpoints that responded with results.

For all others, we parsed the response, and recorded any errors if the
parser concluded the content were invalid.

>>>>

We used SPARQLES survey list of SPARQL endpoints as of 2014-11-17, and
filtered out those deemed unresponsive. This resulted in a
list of 312 endpoints.

@@

We obtained a successful response from a total 2965 information
resources, either with SPARQL results or RDF data. A successful
response is rather strictly defined, not only must there be a
successful HTTP response after redirects are resolved, the response
must also return a valid RDF media type (unless it is a SPARQL result)
and the response must parse into an RDF model.

@@

In Figure~\ref{fig:hardtable}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification \cite{voidnote} also notes that the
statistics are considered estimates.

@@

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\footnote{https://metacpan.org/release/KJETILK/RDF-Generator-HTTP-0.003}
to CPAN. We recorded whether the conditional request showed that the
BTC data were still fresh, and if it was, we retrieved the current
data, as we had not coupled the headers to the body in our original
retrieval.  Based on the resulting headers, we let
libwww\footnote{https://metacpan.org/release/GAAS/libwww-perl-6.04}
calculate both standards-compliant and simple heuristic freshness
lifetime.

If the initial response had RFC7232 headers, we made another
request to see if the server included the headers but does not
support conditional requests. The heuristic we employed is
that if the headers remain the same, but the result was returned,
rather than just a response code \httph{304} (which indicates that the
previous result can be reused), the server does most probably not
support it.

For endpoints, we examined the response message, to see if there are
any results to our query, and recorded that if there are. In addition
to the endpoints registered in the SPARQLES survey, our process found
18~endpoints that responded with results. For all others, we parsed
the response, and recorded any errors if the parser concluded the
content were invalid.
